Plots and tables summarizing results of Poisson simulations

### 2019-12-20 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

```{r plot-cb-function, fig.height=4, fig.width=8}
mu.cb <- 0.01 + cblocks.f(t)
x     <- rpois(n,mu.cb)
create.signal.plot(t,x,mu.cb)
```

@@

```{r plot-bumps-function, fig.height=4, fig.width=8}
mu.b <- 0.01 + bumps.f(t)
x    <- rpois(n,mu.b)
create.signal.plot(t,x,mu.b)
```

>>>>

```{r plot-cb-function, fig.height=2.5, fig.width=8}
mu.cb <- 0.01 + cblocks.f(t)
x     <- rpois(n,mu.cb)
create.signal.plot(t,x,mu.cb)
```

@@

```{r plot-bumps-function, fig.height=2.5, fig.width=8}
mu.b <- 0.01 + bumps.f(t)
x    <- rpois(n,mu.b)
create.signal.plot(t,x,mu.b)
```
